Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2024-10-23 02_paper/02_study/02_expertise_paper/paper_methods.tex
x paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\begin{tabular}{lllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
\midrule
Expert & 42 & 59.52 & 39.31 & 10.64 & 26.00 & 60.00\\
Novice & 42 & 69.05 & 22.83 & 1.85 & 19.00 & 27.00\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llllllllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
\midrule
Expert & 42 & 11.79 & 11.43 & 1.00 & 38.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA\\
Novice & 42 & 0.00 & 0.00 & 0.00 & 0.00 & 6.74 & 2.65 & 3.00 & 11.00 & 9.62 & 7.19 & 0.00 & 36.00 & 88.10 & NA\\
\bottomrule
\end{tabular}

@@

The sample consisted of \emph{N} = 84 participants with \emph{n} = 42 expert teachers and \emph{n} = 42 novice teachers.

@@

The expert teachers (25 women; 59.52\%) had a mean age of 39.30 years (\emph{SD} = 10.60; range: 26-60) and an average teaching experience of 11.80 years (\emph{SD} = 11.40; range: 1-38).
9.52\% of the experts were primary school teachers and 80.95\% were secondary school teachers. NA\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (29 women; 69.05\%) had a mean age of 22.80 years (\emph{SD} = 1.90; range: 19-27) with an average teaching experience of 0 years. On average, the student teachers were in their 6.70 semester (\emph{SD} = 2.60; range: 3-11). Furthermore, they had an average teaching experience of 9.60 teaching units à 45min (\emph{SD} = 7.20; range: 0-36) through the internships during their studies.
21.43\% of the novices were studying to become primary school teachers, 57.14\% to become secondary school teachers and 19.05\% to become special education teachers. 88.10\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

\caption{\label{tab:rating_scales}Table Rating Scales Disruption Factor}

\begin{tabular}{llllll}
\toprule
Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
\midrule
Expert & chatting & 6.44 & 3.33 & 1.00 & 10.00\\
Expert & clicking pen & 5.57 & 2.87 & 0.00 & 10.00\\
Expert & drawing & 1.85 & 1.46 & 0.00 & 6.00\\
Expert & drumming & 4.60 & 2.44 & 1.00 & 8.00\\
Expert & head on table & 3.73 & 2.25 & 0.00 & 8.00\\
Expert & heckling & 7.19 & 2.37 & 2.00 & 10.00\\
Expert & looking at phone & 4.71 & 3.10 & 1.00 & 10.00\\
Expert & snipping & 4.00 & 3.61 & 0.00 & 10.00\\
Expert & whispering & 4.56 & 2.50 & 0.00 & 9.00\\
Novice & chatting & 8.62 & 1.35 & 5.00 & 10.00\\
Novice & clicking pen & 7.00 & 2.11 & 3.00 & 10.00\\
Novice & drawing & 2.24 & 1.48 & 0.00 & 4.00\\
Novice & drumming & 6.57 & 2.27 & 0.00 & 10.00\\
Novice & head on table & 4.09 & 2.09 & 1.00 & 8.00\\
Novice & heckling & 6.96 & 2.57 & 2.00 & 10.00\\
Novice & looking at phone & 3.90 & 1.94 & 1.00 & 8.00\\
Novice & snipping & 4.67 & 3.33 & 0.00 & 9.00\\
Novice & whispering & 6.08 & 2.36 & 1.00 & 10.00\\
\bottomrule
\end{tabular}

\caption{\label{tab:rating_scales}Table Rating Scales Confident Factor}

\begin{tabular}{llllll}
\toprule
Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
\midrule
Expert & chatting & 8.44 & 2.03 & 2.00 & 10.00\\
Expert & clicking pen & 8.93 & 1.00 & 7.00 & 10.00\\
Expert & drawing & 9.23 & 1.36 & 5.00 & 10.00\\
Expert & drumming & 9.07 & 0.96 & 7.00 & 10.00\\
Expert & head on table & 9.00 & 1.41 & 5.00 & 10.00\\
Expert & heckling & 6.75 & 2.89 & 2.00 & 10.00\\
Expert & looking at phone & 9.21 & 1.05 & 7.00 & 10.00\\
Expert & snipping & 9.06 & 1.48 & 4.00 & 10.00\\
Expert & whispering & 8.06 & 2.11 & 3.00 & 10.00\\
Novice & chatting & 6.42 & 2.39 & 0.00 & 10.00\\
Novice & clicking pen & 7.54 & 1.89 & 3.00 & 10.00\\
Novice & drawing & 8.81 & 1.25 & 5.00 & 10.00\\
Novice & drumming & 7.57 & 2.11 & 3.00 & 10.00\\
Novice & head on table & 7.30 & 1.96 & 3.00 & 10.00\\
Novice & heckling & 5.35 & 2.53 & 1.00 & 10.00\\
Novice & looking at phone & 7.65 & 1.73 & 3.00 & 10.00\\
Novice & snipping & 8.04 & 1.73 & 3.00 & 10.00\\
Novice & whispering & 7.25 & 2.03 & 2.00 & 10.00\\
\bottomrule
\end{tabular}

@@

\emph{Monitoring} includes proactive strategies such as omnipresence. This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them. The second strategy is overlapping. In this case, the teacher is able to control several teaching processes at the same time. Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions {[}cf.~ibid.; Kounin (2006), p.~89ff{]}.

@@

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}. The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult. al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M. Barth, 2022), \emph{viridis} (Version 0.6.5; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Monitoring & 4.00 & 0.71 & 0.11 & 0.44 & 0.96 & -0.11 & 3.76 & 0.37\\
Managing Momentum & 5.00 & 0.74 & 0.11 & 0.51 & 0.94 & -0.25 & 2.85 & 0.19\\
Rules and routines & 3.00 & 0.75 & 0.11 & 0.46 & 0.90 & -0.74 & 3.25 & -0.28\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Monitoring & 4.00 & 0.71 & 0.15 & 0.52 & 0.92 & 0.17 & 1.76 & 0.38\\
Managing Momentum & 5.00 & 0.70 & 0.13 & 0.52 & 0.89 & 0.31 & 1.77 & 0.34\\
Rules and routines & 3.00 & 0.70 & 0.13 & 0.47 & 0.89 & -0.27 & 2.20 & 0.46\\
\bottomrule
\end{tabular}

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\begin{tabular}{lllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
\midrule
Expert & 40 & 60.00 & 39.10 & 10.55 & 26.00 & 60.00\\
Novice & 42 & 69.05 & 22.83 & 1.85 & 19.00 & 27.00\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llllllllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
\midrule
Expert & 40 & 11.55 & 11.32 & 1.00 & 38.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 52.00\\
Novice & 42 & 0.00 & 0.00 & 0.00 & 0.00 & 6.74 & 2.65 & 3.00 & 11.00 & 9.62 & 7.19 & 0.00 & 36.00 & 88.10 & NA\\
\bottomrule
\end{tabular}

@@

The sample consisted of \emph{N} = 82 participants with \emph{n} = 40 expert teachers and \emph{n} = 42 novice teachers.

@@

The expert teachers (24 women; 60\%) had a mean age of 39.10 years (\emph{SD} = 10.60; range: 26-60) and an average teaching experience of 11.60 years (\emph{SD} = 11.30; range: 1-38).
10\% of the experts were primary school teachers and 85\% were secondary school teachers and 5\% were vocational school teachers. 52\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (29 women; 69.05\%) had a mean age of 22.80 years (\emph{SD} = 1.90; range: 19-27) with an average teaching experience of 0 years. On average, the student teachers were in their 6.70 semester (\emph{SD} = 2.60; range: 3-11). Furthermore, they had an average teaching experience of 9.60 teaching units à 45min (\emph{SD} = 7.20; range: 0-36) through the internships during their studies.
21.43\% of the novices were studying to become primary school teachers, 59.52\% to become secondary school teachers and 19.05\% to become special education teachers. 88.10\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

@@

\emph{Monitoring} includes proactive strategies such as omnipresence. This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them. The second strategy is overlapping. In this case, the teacher is able to control several teaching processes at the same time. Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions {[}cf.~ibid.; Kounin (2006), p.~89ff{]}. --\textgreater{}

@@

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}. The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{apaTables} (Version 2.0.8; Stanley, 2021), \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult. al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{rstatix} (Version 0.7.2; Kassambara, 2023), \emph{sf} (E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M. Barth, 2022), \emph{viridis} (Version 0.6.5; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Monitoring & 4.00 & 0.68 & 0.13 & 0.17 & 0.96 & -1.15 & 6.34 & 0.53\\
Managing Momentum & 5.00 & 0.72 & 0.13 & 0.22 & 0.94 & -1.55 & 6.75 & 0.53\\
Rules and routines & 3.00 & 0.71 & 0.15 & 0.02 & 0.90 & -2.46 & 12.55 & 0.46\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Monitoring & 4.00 & 0.71 & 0.11 & 0.51 & 0.93 & 0.07 & 2.49 & 0.40\\
Managing Momentum & 5.00 & 0.72 & 0.12 & 0.51 & 0.95 & -0.02 & 1.86 & 0.41\\
Rules and routines & 3.00 & 0.72 & 0.11 & 0.47 & 0.92 & -0.15 & 2.39 & 0.25\\
\bottomrule
\end{tabular}

@@

\bibitem[\citeproctext]{ref-R-rstatix}
Kassambara, A. (2023). \emph{Rstatix: Pipe-friendly framework for basic statistical tests}. Retrieved from \url{https://CRAN.R-project.org/package=rstatix}

@@

\bibitem[\citeproctext]{ref-R-apaTables}
Stanley, D. (2021). \emph{apaTables: Create american psychological association (APA) style tables}. Retrieved from \url{https://CRAN.R-project.org/package=apaTables}
